---
title: "More ggplot Figures Peer Review"
output: html_document
---

# Thomas John James



```{r setup, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
suppressPackageStartupMessages(library(GGally))
suppressPackageStartupMessages(library(RColorBrewer))
suppressPackageStartupMessages(library(ggalt))
suppressPackageStartupMessages(library(ggcorrplot))
```

## Problem 1

Create the figure in the solution for Problem 1, using the data included in the R Markdown file.

```{r problem_1_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK
library(tidyverse)

set.seed(12345)
var1<-runif(50,0,10)
set.seed(12345)
var2<-var1+rnorm(50,5,2)
set.seed(12345)
var3<- var1*(-rnorm(50,1,.2))

dat1<-tibble(var1,var2,var3)


```

```{r problem_1,echo=FALSE,message=FALSE}
ggplot2::ggplot(data = dat1, mapping = ggplot2::aes(x = var1, y = var2)) +
    ggplot2::geom_point(position = "jitter") +
    ggplot2::geom_smooth(formula = y ~ x, method = "loess") +
    ggplot2::labs(x = "Variable1", y = "Variable2")
```

## Problem 2

Create the figure in the solution for Problem 2, using the data included in the R Markdown file.

```{r problem_2_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(10)
var1<-runif(50,0,10)
set.seed(10)
var2<-var1+rnorm(50,5,2)
set.seed(10)
var3<- var1*(-rnorm(50,1,.2))

dat2<-tibble(var1,var2,var3)
```


```{r solution_p2,echo=FALSE,message=FALSE}
# Custom function for the density plots:
my_density <- function(data, mapping) {
    ggplot2::ggplot(data = data, mapping = mapping) +
        ggplot2::geom_density(fill = "blue")
}
# Custom function for the scatter plots:
my_scatter <- function(data, mapping) {
    ggplot2::ggplot(data = data, mapping = mapping) +
        ggplot2::geom_point(color = "orange", position = "jitter")
}
# Plot the figure:
GGally::ggpairs(
    data = dat2,
    diag = list(continuous = my_density),
    lower = list(continuous = my_scatter)
)

```

## Problem 3

Create the figure in the solution for Problem 3, using the data included in the R Markdown file.

```{r problem_3_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(12)
var1<-runif(50,0,10)
set.seed(12)
var2<-var1+rnorm(50,5,2)
set.seed(12)
var3<- var1*(-rnorm(50,1,.2))

dat3<-tibble(var1,var2,var3)
```

```{r problem3,echo=FALSE}
# Compute the correlations:
corrs <- cor(dat3)
# Plot the figure:
ggcorrplot::ggcorrplot(
    corr = corrs,
    title = "Correlations",
    type = "lower"
)
```

## Problem 4

Create the figure in the solution for Problem 4, using the data included in the R Markdown file.

```{r problem_4_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(5678)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat4<-tibble(names,var1)
```

```{r problem_4,echo=FALSE}
ggplot2::ggplot(
    data = dat4,
    mapping = ggplot2::aes(x = var1, y = reorder(names, var1))
) +
    ggplot2::geom_point(size = 5) +
    ggplot2::labs(x = "Variable 1") +
    ggplot2::theme(
        axis.title.y = ggplot2::element_blank(),
        panel.grid.major.x = ggplot2::element_blank(),
        panel.grid.minor.x = ggplot2::element_blank(),
        panel.grid.major.y = ggplot2::element_line(
            color = "red",
            linetype = "dotted"
        )
    )

```

## Problem 5

Create the figure in the solution for Problem 5, using the data included in the R Markdown file.

```{r problem_5_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(13)
var1<-rnorm(10,25,5)
names<-letters[1:10]

dat5<-tibble(names,var1)
```

```{r problem_5,echo=FALSE}
ggplot2::ggplot(
    data = dat5,
    mapping = ggplot2::aes(x = reorder(names, var1), y = var1)
) +
    ggplot2::geom_point(color = "darkgreen") +
    ggplot2::geom_segment(
        x = names,
        xend = names,
        y = 0,
        yend = var1,
        color = "darkgreen"
    ) +
    ggplot2::labs(y = "Variable 1") +
    ggplot2::theme(
        axis.text.x = ggplot2::element_text(angle = 90),
        axis.title.x = ggplot2::element_blank()
    ) +
    ggplot2::scale_y_continuous(limits = c(0, 35))

```

## Problem 6

Create the figure in the solution for Problem 6, using the data included in the R Markdown file.

```{r problem_6_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

set.seed(8)
fiction<-tibble(Genre=rep("Fiction",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(7)
biography<-tibble(Genre=rep("Biography",5),Time=seq(1:5),Total=sample(1:10,5))
set.seed(9)
mystery<-tibble(Genre=rep("Mystery",5),Time=seq(1:5),Total=sample(1:10,5))

books_checked_out<-bind_rows(fiction,biography,mystery)
```

```{r problem_6,echo=FALSE}
ggplot2::ggplot(
    data = books_checked_out,
    mapping = ggplot2::aes(x = Time, y = Total, fill = Genre)
) +
    ggplot2::geom_area() +
    ggplot2::labs(title = "Books Checked Out")

```

## Problem 7

Create the figure in the solution for Problem 7, using the data included in the R Markdown file.

```{r problem_7_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

books_checked_out2 <- books_checked_out %>%
  filter(Time==1 | Time==5) %>%
  pivot_wider(names_from = Time,values_from=Total) %>%
  rename(Time1=`1`,Time5=`5`)
```
   
```{r,problem_7,echo=FALSE,message=FALSE}   
ggplot2::ggplot(
    data = books_checked_out2,
    mapping = ggplot2::aes(x = Time1, xend = Time5, y = reorder(Genre, Time1))
) +
    ggalt::geom_dumbbell(
        colour_x = "red",
        size_x = 3,
        colour_xend = "purple",
        size_xend = 3
    ) +
    ggplot2::labs(y = "Genre") +
    ggplot2::theme(axis.title.x = ggplot2::element_blank())

```

## Problem 8

Create the figure in the solution for Problem 8, using the data included in the R Markdown file.

```{r, problem_8_data,include=FALSE}

#####DO NOT MODIFY THIS CHUNK

pie_dat<-c(1,2,3,4,5)
```

```{r, problem_8,echo=FALSE}


###HINT: check the Help file for pie to see how to specify the color to the my_color palette

library(RColorBrewer)

my_color<-brewer.pal(5,"Spectral")

pie(pie_dat, col = my_color)

```


